### 2013-12-16 article2013.Rmd
Puristin kaikki mallit yhteen taulukkoon

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB contextual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                      "IB contextual",
                      "IB all")

texreg(list(soc.0,soc.1,soc.Cont,soc.4,
            ind.0,ind.1,ind.Cont,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

```{rarticleModelsFull, results='asis', eval=TRUE}
load("data/finalModels.RData")

>>>>

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB contextual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                      "IB contextual",
                      "IB all",
                      "SB vs. IB")

texreg(list(soc.0,soc.1,soc.Cont,soc.4,
            ind.0,ind.1,ind.Cont,ind.4,socVsInc),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

```{rarticleModelsFull, results='asis', eval=FALSE}
load("data/finalModels.RData")
